New lower bounds for Schur and weak Schur numbers

### 2021-05-02 article/introduction.tex
state of the art

\par
As for smaller numbers, the best lower bounds were obtained by conducting a computer search. This search for 
weakly sum-free partitions relied on the recursive assumption that a good weakly sum-free partition into \(n+1\) 
colors starts with a good weakly sum-free partition into \(n\) colors.

>>>>

\par
As for smaller numbers, the best lower bounds were obtained by conducting a computer search. Eliahou \cite{ELIAHOU2012175}, 
Rafilipojaona \cite{Rafilipojaona} and Bouzy \cite{Bouzy2015AnAP} improved lower bounds with Monte-Carlo methods. It 
has been the main approch in the previous decade. 
This search for weakly sum-free partitions relied on the recursive assumption that a good weakly sum-free partition into \(n+1\) 
colors starts with a good weakly sum-free partition into \(n\) colors. This assumption was necessary in order for the Monte-Carlo
approch to yield results. However, we show in the \hyperlink{sat}{last section} how this search space may not countain
the optimal solution. Thus further work using similar methods might need to put that assumption aside and 
find a different search space.

### 2021-05-02 article/search_space.tex
state of the art

\qquad In this section, we first provide evidence which indicate that the main assumption made by papers which
found the previous best known lower bounds for weak Schur numbers using a computer may not be correct. 
This is done primarily by studying \(\WS(6)\). Then, in an effort to eliminate irrelevant search spaces, we 
obtain stronger results than those previously known for \(\WS (5)\) while gaining several orders of magnitude 
in computation time by giving additional information to the SAT solver without losing in generality. In this 
section, we assume that the subsets are ordered.

>>>>

\qquad \hypertarget{sat}{In} this section, we first provide evidence which indicate that the main assumption made by papers which
found the previous best known lower bounds for weak Schur numbers using a computer may not be correct. 
This is done primarily by studying \(\WS(6)\). Then, in an effort to eliminate irrelevant search spaces, we 
obtain stronger results than those previously known for \(\WS (5)\) while gaining several orders of magnitude 
in computation time by giving additional information to the SAT solver without losing in generality. In this 
section, we assume that the subsets are ordered.
